---
title: "Regression"
author: "Scott Stoltzman"
date: "6/3/2019"
output:
  html_document: default
  pdf_document: default
---

```{r}
library(tidyverse)
library(ggiraphExtra)
library(broom)
library(MASS)
library(ISLR)
```

### Explore your data set  
Take a look in your `Help` panel (in RStudio) to see the descriptions of the fields
```{r}
?Boston
```

### View your data
```{r}
data = as_tibble(Boston)
head(data)
```

### We will attempt to model the `medv` data - the median value of owner-occupied homes (in $1000s)

Plot the `lstat` on the x and `medv` on the y axis in a scatter plot.
```{r}
data %>%
  ggplot(data, mapping= aes(x=lstat, y= medv)) +
  geom_point()

```


### Build a model to predict `medv`
Do single linear regression utilizing `lm` 
```{r}
model_1 = lm(medv ~ lstat, data = data)
model_1
```


### Show a better description of the model
```{r}
summary(model_1)
```


### Interpret what your results above mean:

< Homework >

This tells us that there is a strong statistical correlation between lstat and medv.





### Can you display the confidence intervals?
```{r}
confint(model_1)
```

### Interpret what your results above mean:

< Homework >

I honestly don't know what is going on here



### Predict points for lstat values of c(5, 10, 15)
```{r}
predict_points = tibble(lstat = c(5, 10, 15))
predict(model_1, predict_points , interval= 'prediction')
```


### Plot your first model
```{r}
ggPredict(model_1)+
  geom_smooth()
```


### Create a model using both `lstat` and `age`
```{r}
model_2 = lm(medv ~ lstat + age, data = data)
summary(model_2)
```


### Interpret what your results above mean:

< Homework >

That there is also a strong statistical correlation between lstat and age.  I feel okay about this model.  The Multiple R-squared and adjusted R-squared aren't great.  the p-value good.  It's not terrible.  But there is clearly better.

### Create a model using all variables as predictors
```{r}
model_3 = lm(medv ~., data = data)
summary(model_3)
```

### Interpret what your results above mean:

< Homework >

The strongest correlations are medv, age, rm.  rad, dis, zn and ptratio also are strongly correlated.  Very good Multiple R-squared and Adjusted R-squared values.  There are better models in this assignment if I am only looking at the F-statistic.  But I would feel very good about this model overall.


### How do these numbers compare with those from `model_2` ?

< Homework >

Model 2

age          0.15281    0.00902  16.940  < 2e-16 ***

Model 3

age          0.073206   0.010117   7.236 1.79e-12 ***

### Create a model with an interaction term
Use `lstat` and `age` to predict `medv`
```{r}
model_4 = lm(medv ~ lstat + age + lstat*age, data = data)
summary(model_4)
```


### Interpret what your results above mean:

< Homework >

This is a good model.  I can tell by the PR codes and the 


### Create a model using `lstat` and `lstat ^ 2`
```{r}


model_5 = lm(medv ~ lstat + I(lstat^2), data = data)
summary(model_5)
```


### Interpret what your results above mean:

I can tell this is an even better model than model 4 because our Multiple R-squared, Adjusted R-squared, F-statistic all improved while the p-value stayed at <2.2e-16 which is really good.


### Is your model still linear?

< Homework >




### Plot your model's fitted values  
The tibble `data_model` has been created for you with the predictions in a column called `medv_predictions`
```{r}
data_model = data %>%
  mutate(medv_predictions = fitted(model_5))

data_model %>%
  ggplot(aes(x=lstat)) +
  geom_point(aes(y=medv)) + 
  geom_point(aes(y=medv_predictions), color='red')
```

### Interpret what your results above mean:

< Homework >

The black dots are the actual intersects of medv and lstat where the red dots (which form a curved line) show where the intersects would be if they perfectly matched the model.
